% Set up Font
\definefallbackfamily [mainface] [rm] [Noto Emoji] [range={miscellaneoussymbols,dingbats,miscellaneoussymbolsandpictographs}]
\definefontfamily     [mainface] [rm] [LM Roman 10]
\setupbodyfont        [mainface]
\enabletrackers[fonts.missing]

% Enable X11 Colors
\usecolors[xwi]

% Turn off page numbering
\setuppagenumbering[location=]

\setuplayout
  [header=0pt,
   margin=0pt,
   footerdistance=0cm,
   topspace=1cm,
   backspace=1cm,
   width=fit,
   % margin bottom of text to paper
   height=\dimexpr
    \paperheight-\topspace+\footerheight+\footerdistance-5cm\relax]

% Configure title
\setuphead[title][
    align=center,
    after={\blank[0cm]},
    color=steelblue]

% Configure section headers
\setuphead[subject][
    after={\hrule \blank[small]},
    style=bold,
    color=steelblue]

\setuphead[subsubject][
    after={\blank[none]},
    before={\blank[medium]},
    style=bold]

% Configure itemize
\setupitemize[1][packed][
    before={\blank[none]},
    leftmargin=0.7cm,
    symbol=2]  % symbol 2 or 5


\starttext

%%%%%%%%%%%%%%%%%%%%%%%
% General Information %
%%%%%%%%%%%%%%%%%%%%%%%
\starttitle[title=Bryce Kellogg]
\startalignment[middle]

%TODO: hfill but with big margins

\utfchar{"1F4F1} (425) 275-8979 \| \utfchar{"2709} kelloggbryce@gmail.com

\stopalignment
\stoptitle

%%%%%%%%%%%%%
% Education %
%%%%%%%%%%%%%
\startsubject[title=EDUCATION]

    {\bf University of Washington}

\startitemize[symbol=0,leftmargin=0.5cm]
    \item Master's of Science in Electrical Engineering   \hfill GPA: 3.84  \hfill June 2016
    \item Bachelor's of Science in Electrical Engineering \hfill GPA: 3.86  \hfill June 2013
    \item Bachelor's of Science in Computer Engineering   \hfill GPA: 3.86  \hfill June 2013
\stopitemize

\stopsubsubsubject
\stopsubject

%%%%%%%%%%%%%%%%%%%
% Work Experience %
%%%%%%%%%%%%%%%%%%%
\startsubject[title=INDUSTRY EXPERIENCE]


    % Jeeva
    \startsubsubject[title={Jeeva Wireless \hfill {\small March 2015 - Current}}]

        {\it Startup reimagining connectivity for ultra-low power IoT}

        {\bf Director of Engineering & Co-Founder }
        \startitemize
            \item Designed products
            \item FPGA implementation stuff
            \item AWS Cloud Computing stuff
        \stopitemize

    \stopsubsubject


    % UW Grad Student
    \startsubsubject[title={UW Mobile Systems Lab \hfill {\small June 2013 - May 2017}}]

        {\it Does stuff with wireless power, low power communication}

        {\bf Graduate Researcher}
        \startitemize
            \item Lead projects with undergrads
            \item Hacked the Linux Kernel
            \item Implemented Wi-Fi protocol
            \item Wrote ultra-low power code
        \stopitemize

    \stopsubsubject

    % Xilinx Intern
    \startsubsubject[title={Xilinx Inc. \hfill {\small August 2011 - August 2012}}]

        {\it Largest FPGA Manufacturer in the world}

        {\bf Test and Validation Intern}
        \startitemize
            \item Developed Linux kernel device drivers for ARM peripherals.
            \item Designed and deployed unit test and continuous integration framework ARM/FPGA platform.
            \item Wrote Verilog unit tests for FPGA fabric
            \item Debugged ARM microcontroller peripheral issues
        \stopitemize

    \stopsubsubject

\stopsubject

%%%%%%%%%%
% Skills %
%%%%%%%%%%%
\startsubject[title=TECHNICAL SKILLS]

    \startitemize[columns,three]
        \item C/C++
        \item D
        \item Java
        \item Verilog
        \item Wireless Communication
        \item System Design
        \item HTML
        \item Javascript
        \item ARM
        \item FPGA
        \item Wireless Power
        \item Python
        \item Wi-Fi
        \item Git
        \item Matlab
    \stopitemize

\stopsubject

%%%%%%%%%%%%%%%%
% Publications %
%%%%%%%%%%%%%%%%
\page
\startsubject[title=PUBLICATIONS]

{\bf LoRa Backscatter: Enabling the Vision of Ubiquitous Connectivity} \crlf
Vamsi Talla, Mehrdad Hassar, Bryce Kellogg, Ali Najafi, Josh Smith, and Shyam Gollakota.\crlf
{\it Ubicomp, 2017} \crlf

{\bf Battery-free Cellphone} \crlf
Vamsi Talla, Bryce Kellogg, Shyam Gollakota, and Josh Smith. \crlf
{\it Ubicomp 2017} \crlf

{\bf Inter-Technology Backscatter: Towards Internet Connectivity for Implanted Devices} \crlf
Vikram Iyer, Vamsi Talla, Bryce Kellogg, Shyam Gollakota, and Josh Smith. \crlf
{\it SIGCOMM 2016} \crlf

{\bf Passive Wi-Fi: Bringing Low Power to Wi-Fi Transmissions} \crlf
Bryce Kellogg, Vamsi Talla, Shyam Gollakota, and Josh Smith. \crlf
{\it NSDI 2016 } \crlf

{\bf Powering the Next Billion Devices With Wi-Fi} \crlf
Vamsi Talla, Bryce Kellogg, Ben Ransford, Saman Naderiparizi, Shyam Gollakota, and Josh Smith. \crlf
{\it ACM CoNext 2015} \crlf

{\bf Wi-Fi Backscatter: Internet Connectivity for RF-Powered Devices} \crlf
Bryce Kellogg, Aaron Parks, Shyam Gollakota, Josh Smith, and David Wetherall.  \crlf
{\it SIGCOMM 2014} \crlf

{\bf Bringing Gesture Recognition to All Devices} \crlf
Bryce Kellogg, Vamsi Talla, and Shyam Gollakota. \crlf
{\it NSDI, 2014} \crlf

\stopsubject

\stoptext

